### 2018-08-01 VV570/PROJ2/tex/report.tex
task3 partly ok

\section{Task 2}
	With trival inequality analysis, the exact solution is given as $x=[0.5, 0, -\frac{\pi}{6}]$, which can be used for varification.\\
	In general, the initial value for such a non-linear system is hard to know, even the range for each component is hard to estimate. In this case, the downhill simplex method can be applied to produce a fine inital guess for further calculation like newton or quasi-newton.\\
	Numerical experiments were done to identify the difference in terms of time cost.

>>>>

\section{Task 2}
	With trival inequality analysis, the exact solution is given as $x=[0.5, 0, -\frac{\pi}{6}]$, which can be used for varification.
	\subsection{Solve directly}
		Applying the fixed-point iteration, newton's method and the broyden's method to this non-linear system respectively, ...(TODO)
	\subsection{Downhill simplex algorithm}
	In general, the initial value for such a non-linear system is hard to know, even the range for each component is hard to estimate. In this case, the downhill simplex method can be applied to produce a fine inital guess for further calculation like newton or quasi-newton.
	\subsection{Solve with initialization}

	Numerical experiments were done to identify the difference in terms of time cost.
